\documentclass[]{friggeri-cv}

\begin{document}

\header{Jakub}{Kadlčík}{opensource enthusiast \& developer}


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
Mahenova~635
Jeseník,~790~01
Czech Republic
~
+420~730~653~527
\href{mailto:frostyx@email.cz}{frostyx@email.cz}
~
\href{http://frostyx.cz}{frostyx.cz}
\href{https://github.com/FrostyX}{github.com/FrostyX}
\section{Languages}
Czech as native language
Fluent English
\section{Programming}
{\color{red} $\varheartsuit$} Python
PHP (Laravel), Java,
C++, LaTeX, Bash
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

\entry
{2012--now}
{Bachelor {\normalfont of Computer Science}}
{Palacký University, Olomouc}
{\emph{Determine applications affected by upgrade} \\ This thesis deals with the problem of finding running applications on GNU/Linux which need restart after system update.}

\entry
{2008--2012}
{{\normalfont High school}}
{SPŠ Bruntál}
{Specialization in information technologies}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\subsection{Part Time}
\begin{entrylist}

\entry
{2014--2016}
{FMRI laboratory of Palacky University}
{Olomouc, Czech Republic}
{\emph{Linux Administrator} \\
I took care of multiple workstations running on Debian and I was responsible for solving user issues. In spare time I was developing new online register for examinations.}

\entry
{2009--2012}
{Creative-Vision.cz}
{Bruntál, Czech Republic}
{\emph{Web Developer} \\
I Worked as backend developer of web applications and mainly used technologies such as PHP and MySQL.}

\entry
{2009--2012}
{SPŠ Bruntál}
{Bruntál, Czech Republic}
{\emph{Network Administrator} \\
This was unpaid work experience. I was responsible for providing network connection to about hundred students in the hostel. It included running DHCP, firewall, data server, etc.}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{entrylist}

\entry
{2013--now}
{Tracer}
{\href{http://tracer-package.com}{tracer-package.com} | \href{https://github.com/FrostyX/tracer}{github.com/FrostyX/tracer}}
{Tracer determines which applications use outdated files and recommends to restart them. This project started as my bachelor thesis.}

\entry
{2014}
{Lazy Snake}
{\href{http://lazysnake-frostyx.rhcloud.com/}{lazysnake-frostyx.rhcloud.com} | \href{https://github.com/FrostyX/lazy-snake}{github.com/FrostyX/lazy-snake}}
{Lazy Snake is a web based, easy to use and nice looking python profiler. It runs on OpenShift and was created as a competition project for Winter of Code organized by the DevConf.cz}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:} programming, GNU/Linux, opensource
\\
\textbf{Personal:} running, cycling, healthy lifestyle, reading

\end{document}
